EasyMerge - Clone Code Refactor

### 2014-03-06 paper/paper.tex
added something to introduction

Clone detection has been an avid research topic in the field of software engineering for decades. Fortunately, several automated techniques for detecting code clones
have already been proposed.

>>>>

Clone detection has been an avid research topic in the field of software engineering for decades. Fortunately, several automated techniques for detecting code clones
have already been proposed. However, how to deal with detected clones, e.g. how to distinguish necessary clones from unnecessary ones and how to refactor code to remove
unnecessary clones still remain a big problem in not only commercial but also academic domain. As a result, in this paper, we try to classify code clones and build
a recommendation system called EasyMerge to help developers merge unnecessary clones on top of current state-of-the-art clone detection approach.
